---
title: "Interactive penguins"
author: "Tiffany Hsu"
date: "10/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load packages
library(tidyverse)
library(palmerpenguins)
library(plotly)
library(DT)
library(here)
```

Create a scatterplot of penguin flipper_length_mm (x-axis) versus body_mass_g (y-axis) with points having different colors based on species
 
```{r}
penguins_graph <- ggplot(data = penguins, 
       aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species))

# make the scatterplot interactive with the plotly package
ggplotly(penguins_graph)


penguins_graph
```

## Make a nicer table with `DT` package

```{r}
# creates searchable and organized table from a dataframe
datatable(penguins)
```

### .gitignore
- add *.html to ignore saving any html files when you knit (asterisk applies to everything)

### Creating column graoh and save with `ggsave()`
I am going to make a column graph using `geom_bar` of counts of penguins by island with fill color indicating penguin species. Then save that using `ggsave()`

```{r}
ggplot(data = penguins, aes(x = island)) + 
  geom_bar(aes(fill = species))

# use `ggsave()` to tell it how to save (size, resolution, etc), use here() to tell it where to save and the new file name
ggsave(here("final_figures", "island_counts.png"))

```



